\begin{enumerate}
	\item Siregar,S. B.,2007. Fattening Cattle. Jakarta : Penebar Swadaya.
	\item Soeprapto,H., Z.Abidin. 2006. How Fattening Beef Cattle. Jakarta : Agromedia Press
	\item  M. D. Deddy B. Lasfeto, "A measuring weight model of timor's beef cattle based on image," International Journal of Engineering and Technology (IJET), p. 12. 
	\item T. M. Banhazi, "Weight Estimation Using Image Analysis and Statistical Modelling: A Preliminary Study," Applied engineering in agriculture, 2007.
	\item Mehrotra, R., and S. Zhan. 1996. A computational approach to zero-crossing-based two-dimensional edge detection. Graphical Models and Image Processing 58(1): 1-17.
	\item Z. H. Pradana, B. H. and S. D., "Beef Cattle Weight Determine By Using Digital Image Processing," The 2016 International Conference on Control, Electronics, Renewable Energy and Communications (ICCEREC), 2016.
	\item A. Yamashita, "Estimation of Calf Weight from Fixed-Point Stereo Camera Images Using Three Dimensional Successive Cylindrical Model," Proceedings of the 5th IIAE International Conference on Intelligent Systems and Image Processing 2017, 2017.
	\item Zhou, B. (n.d.). Learning Deep Features for Discriminative Localization. Retrieved from \url{http://cnnlocalization.csail.mit.edu/Zhou_Learning_Deep_Features_CVPR_2016_paper.pdf}


	\item R. Dalai and K. K. S. , "Weight Estimation through Image Analysis," International Journal of Computer Trends and Technology (IJCTT), vol. 49, pp. 1-5, July 2017.
\end{enumerate}